---
title: "lambdaR - Lambda expressions in R"
author: "Koji MAKIYAMA"
output: 
  html_document:
    keep_md: true
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Overview

With this package, you can use lambda expressions in R:

```{r}
library(lambdaR)
library(dplyr)
1:10 %>% Filter_(x: x %% 2 == 0) %>% Map_(x: x ** 2) %>% Reduce_(x,y: x + y)
```

You can use placeholders:

```{r}
1:10 %>% Filter_(._ %% 2 == 0) %>% Map_(._ ** 2) %>% Reduce_(._ + ._)
```

And you can write like below:

```{r}
is_even <- lambda(._ %% 2 == 0)
square <- lambda(._ ** 2)
add <- lambda(._ + ._)
1:10 %>% Filter_(is_even) %>% Map_(square) %>% Reduce_(add)
```

## How to install

```{r, eval=FALSE}
install.packages("devtools") # if you have not installed "devtools" package
devtools::install_github("hoxo-m/lambdaR")
```

## Usage

### lambda()

`lambda()` function is to enable using lambda expressions in R:

```{r}
increment <- lambda(x: x + 1)
add <- lambda(x,y: x + y)
```

That allows to redefine higher order functions using lambda expressions.

### Application

We redefined higher order functions:

- `Filter()` to `Filter_()`
- `Map()` to `Map_()`
- `Reduce()` to `Reduce_()`
- `Find()` to `Find_()`
- `Position()` to `Position_()`
- `Negate()` to `Negate_()`

You can input lambda expressions to these functions:

#### Filter_()

```{r}
1:10 %>% Filter_(x: x %% 2 == 0)
```

#### Map_()

```{r}
1:10 %>% Map_(x: x ** 2) %>% unlist
```

```{r}
list(1:5, 6:10) %>% Map2_(x,y: x + y) %>% unlist
```

#### Reduce_()

```{r}
1:10 %>% Reduce_(x,y: x + y)
```

#### Find_()

```{r}
LETTERS %>% Find_(x: tolower(x) == "f")
```

#### Position_()

```{r}
LETTERS %>% Position_(x: x == "F")
```

#### Negate_()

```{r}
1:10 %>% Filter_(Negate_(x: x %% 2 == 0))
```

#### placeholders

And also you can use placeholders:

```{r}
1:10 %>% Filter_(._ %% 2 == 0)
```

```{r}
1:10 %>% Map_(._ ** 2) %>% unlist
```

```{r}
list(1:5, 6:10) %>% Map2_(._ + ._) %>% unlist
```

```{r}
1:10 %>% Reduce_(._ + ._)
```

```{r}
LETTERS %>% Find_(tolower(._) == "f")
```

```{r}
LETTERS %>% Position_(._ == "F")
```

```{r}
1:10 %>% Filter_(Negate_(._ == 0))
```
